Twitter network data mining with R
===

[@dzidorius (Dzidas)](http://twitter.com/dzidorius)


fork code from  
[https://github.com/kafka399/haxogreen.lu](https://github.com/kafka399/haxogreen.lu) 

Prerequisite for R
===

    requirements=c('twitteR','tm','wordcloud','RColorBrewer')  
    if(length(requirements[which(!(requirements %in% 
		installed.packages()[,1]))])>0)  
        install.packages(requirements[which(!(requirements %in% 
		installed.packages()[,1]))])
Get the data
===

Who is tweeting about #Haxogreen

```{r results=asis,comment=NA, message=FALSE}
require(twitteR)
#tweets=twitteR::searchTwitter('#haxogreen',n=2000)
load('tweets.Rdata')
names=sapply(tweets,function(x)x$screenName)
rez=(aggregate(names,list(factor(names)),length))
rez=rez[order(rez$x),]
#rownames(rez)=NULL
colnames(rez)=c('name','count')
#only for presentation
options(xtable.type = 'html')
require(xtable)
xtable(t(tail(rez,6)))
```

Plot top10 tweeters
===
```{r topspam, figure=TRUE,fig.cap=''}
barplot(tail(rez$count,10),names.arg=as.character(tail(rez$name,10)),cex.names=.7,las=2)
```

Who are these people
===
```{r results=asis,comment=NA, message=FALSE}
# users=lookupUsers(as.character(tail(rez,3)$name))
load('users.Rdata')
users=lapply(users,function(x){
  if(any(sapply(as.character(tail(rez,3)$name),function(y){
    x$screenName==y})))return(x)})

users=users[!sapply(users,is.null)]

for(i in 1:length(users))
{
cat(paste("**",users[[i]]$name," @",users[[i]]$screenName,"**", "\n===\n",sep=""))
cat(paste("![](http://api.twitter.com/1/users/profile_image?screen_name=",users[[i]]$screenName,
          "&size=normal)",sep=''))
cat(paste("  \n**Created:** ",users[[i]]$created,
          "  \n**Spam rate:** ",round(users[[i]]$followersCount/users[[i]]$friendsCount,digits=2),
          "  \n**Activity:** " , users[[i]]$statusesCount,
          "  \n**Location:** ", users[[i]]$location,"  \n",users[[i]]$description,"  \n",
          "**Last status:** ",(users[[i]]$lastStatus$text),"\n\n",sep=""))
}
```
Exploring similarities - code
===

```{r results=asis,comment=NA, message=FALSE}
##of line version
#users=lookupUsers(as.character(tail(rez,10)$name))
load('users.Rdata')

#friends=sapply(seq(1:10),function(x){(users[[x]]$getFriends())})
load('friends.Rdata')
matrix=matrix(nrow=10,ncol=10)
rez=apply(combn(1:10,2),2,function(x)
{

matrix[x[1],x[2]]=length(which(sapply(friends[[x[2]]],function(x)x$screenName)%in%sapply(friends[[x[1]]],function(x)x$screenName)))/length(friends[[x[2]]])
})

rez3=apply(combn(1:10,2),2,function(x)
{

matrix[x[1],x[2]]=length(which(sapply(friends[[x[1]]],function(x)x$screenName)%in%sapply(friends[[x[2]]],function(x)x$screenName)))/length(friends[[x[1]]])
})

#rez2=combn(1:10,2)[,which(rez>.2)]

pairs=data.frame(pairs=apply(combn(1:10,2)[,which(rez>.4)],2,function(x){paste(users[[x[1]]]$name,'~',users[[x[2]]]$name)}),rate=rez[which(rez>.4)])

pairs=rbind(pairs,data.frame(pairs=apply(combn(1:10,2)[,which(rez3>.4)],2,function(x){paste(users[[x[1]]]$name,'~',users[[x[2]]]$name)}),rate=rez3[which(rez3>.4)]))
```
Exploring similarities
===
```{r results=asis,comment=NA, message=FALSE}
xtable(pairs[order(pairs$rate),])
```
Exploring dissimilarities - code
===

```{r results=asis,comment=NA, message=FALSE}
pairs=data.frame(pairs=apply(combn(1:10,2)[,which(rez<.007)],2,function(x){paste(users[[x[1]]]$name,'~',users[[x[2]]]$name)}),rate=rez[which(rez<.007)])

pairs=rbind(pairs,data.frame(pairs=apply(combn(1:10,2)[,which(rez3<.007)],2,function(x){paste(users[[x[1]]]$name,'~',users[[x[2]]]$name)}),rate=rez3[which(rez3<.007)]))

```
Exploring dissimilarities
===
```{r results=asis,comment=NA, message=FALSE}
xtable(pairs[order(pairs$rate),])
```

Word cloud - code
====

```{r results=asis,comment=NA, message=FALSE}
#tweets=twitteR::searchTwitter('#haxogreen',n=2000)
load('tweets.Rdata')
tweets=sapply(tweets,function(x)x$text)
tweets=tweets[which(!unlist(sapply(seq(2:length(tweets)),function(x){tweets[x]==tweets[x-1]})))+1]
require('tm')
corpus=Corpus(VectorSource(tweets),readerControl=list(language='en'))
corpus=tm_map(corpus,tolower)
corpus=tm_map(corpus,removePunctuation)
corpus=tm_map(corpus,removeWords,c(stopwords('english'),'rt'))

corpus.matrix=TermDocumentMatrix(corpus)
corpus=removeSparseTerms(corpus.matrix,0.75)

rez=sort(rowSums(as.matrix(corpus.matrix)))
rez=data.frame(name=names(rez),count=as.numeric(rez))
rez=rez[-which(rez$name=='haxogreen'),]
```
Word cloud 
===
```{r figure=TRUE,fig.cap='',comment=NA, message=FALSE}
require(RColorBrewer)
require(wordcloud)
wordcloud(rez$name,rez$count, min.freq=7,colors=brewer.pal(8,"Dark2"))
```

Who Am I?
====

Dzidorius Martinaitis
 
> <font color = "grey">Java, C++ and R developer & data junkie</font>


+ blog:    [investuotojas.eu](http://www.investuotojas.eu)
+ twitter: [@dzidorius](http://www.twitter.com/dzidorius)
+ github:  [kafka399](http://https://github.com/kafka399)
+ linkedin: [dzidorius](http://lu.linkedin.com/in/dzidorius)